HealpixNet: Efficient spherical Convolutional Neural Networks with Healpix sampling for cosmological applications

### 2018-06-19 scnn.tex
small text from the meeting
small update in plots

\section{TODO list}
\begin{itemize}
    \item Michael, do you agree with the title HealpixNet
    \item
\end{itemize}

@@

>>>>

\section{TODO list}
\begin{itemize}
    \item Michael, do you agree with the title HealpixNet
    \item Emphaise the novelty of using it on Helapix in abstract, into and rest of the paper
    \item Finish section on Convolutions on graphs (Michael - Nathanael)
    \item Plot of the new filters from Mass maps (Michael)
    \item (done!, plot to be added) check the power spectrum after smoothing
    \item upgrade the plot of pooling (Nathanael)
    \item new plot for network structure (teaser plot) (Michael)
    \item add info on comparison with histogram, so that it's just a demonstration
    \item (done!) Figure 1 to be round
    \item finish section on Efficient convolutions (Nathanael)
    \item conclusions
    \item (done!) new simulations with 3 arcmin smoothing
    \item (done!) simulation with cross-validation for the histogram
    \item (Almost done!) Update result section according to the new simulations...
    \item (Almost done!) simulation PSD
    \item (done!) Results figure, add sigma8
    \item possibly move the eigen decomposition and heat into appendix + add discussion (Nathanael)
\end{itemize}

@@

\begin{itemize}
	\item Spherical CNN has the advantage to have some geometry information => one of the reason better than histogram
	\item PSD...
\end{itemize}

\citep{patton2017cosmologicalconstraints}
